Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-12 papers/paper-eccentricity/paper-eccentricity.tex
Edit sec 3.3 some more

To mimic the nearly linearly plunging orbits before the scattering event seen in \autoref{fig:orbit},
we specify the initial conditions as 
\begin{align}
\vb{x}_0 &= (25\,\mathrm{pc}, b)\\
\dot{\vb{x}}_0 &= (-v_0, 0).
\end{align}
Based on the simulations, we set $v_0 = 450\,\mathrm{km\,s^{-1}}$ to match the
typical SMBH relative velocity at this separation in the $e_0=0.90$ case,
and $v_0 = 560\,\mathrm{km\,s^{-1}}$ to match the $e_0=0.99$ case.
The spheroid eccentricity parameter is not easily measurable from the simulations,
due to stellar components that remain bound to the SMBHs and obscure the background
potential relevant for the dynamics,
as well as due to the potential in the simulations being constantly evolving.
We therefore perform calculations with different values of $e_\mathrm{s}$,
finding a good fit to simulation results for $e_\mathrm{s}\approx 0.9$.

@@

Overall we can however see that this simple model correctly captures the behavior of eccentricity seen in the simulations.
We can therefore use the model to understand the cause of the complicated dependence of the binary eccentricity
on the deflection angle $\theta_\mathrm{defl}$.
\autoref{fig:model_orbits} shows sets of orbits computed with the model for two different potential shapes,
with the parameters otherwise as in the model that matches the $e_0=0.90$ simulation results.
In the $e_\mathrm{s}=0.9$ case the shape of the orbit after the initial scattering depends strongly on the deflection angle,
as the asymmetric potential causes torque on the SMBHs that are not moving along the main axes of the potential.
On the other hand, in the more symmetric potential with $e_\mathrm{s}=0.2$,
the orbit shape is not very sensitive to the deflection angle due to the symmetry of the system,
and the binary always reaches extremely high eccentricities.

>>>>

To mimic the nearly linearly plunging orbits before the scattering event seen in \autoref{fig:orbit},
we specify the initial conditions as 
\begin{align}
\vb{x}_0 &= (25\,\mathrm{pc}, b)\\
\dot{\vb{x}}_0 &= (-v_0, 0).
\end{align}
Based on the simulations, we set $v_0 = 450\,\mathrm{km\,s^{-1}}$ to match the
typical SMBH relative velocity at this separation in the $e_0=0.90$ case,
and $v_0 = 560\,\mathrm{km\,s^{-1}}$ to match the $e_0=0.99$ case.
The spheroid eccentricity parameter $e_\mathrm{s}$ is not easily measurable from the simulations,
due to stellar components that remain bound to the SMBHs and obscure the background
potential relevant for the dynamics,
as well as due to the potential in the simulations being constantly evolving.
However, only sufficiently large values of $e_\mathrm{s}$ allow for low binary
eccentricities to be produced,
as is shown by \autoref{fig:model_orbits}.
Performing calculations with different values of $e_\mathrm{s}$,
we found a good fit to simulation results for $e_\mathrm{s}\approx 0.9$.

@@

Otherwise the behavior of the simulation data is captured well,
with the model correctly producing the two main eccentricity minima,
as well as the $e\approx 1$ region between them.
The minima occur for trajectories where the torque from the background potential together with the dynamical friction
causes the SMBHs to loop around into a nearly circular orbit,
while highly eccentric binaries are produced when the binary is trapped into nearly radial oscillations along the 
the main axes of the potential, as is seen in \autoref{fig:model_orbits}.
